Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-30 manuscript/ERL_global_C_review.Rmd
complete draft!

**Our study reveals that most C fluxes quickly increase to a plateau as stands age...**
@anderson-teixeira_altered_2013

**(paragraph on NEP): **

NEP increases with log(age) to 100 --> strongest C sinks are established secondary forests. (But presumably this exact number is an artifact; don’t over-emphasize.)

Our findings are largely consistent with, but built from a far larger dataset than, those of Pregitzer and Euskirchen (2004 http://dx.doi.org/10.1111/j.1365-2486.2004.00866.x), who found that NPP and NEP to be higher in intermediate-aged forests than older forests, and emphasize the importance of forest age at the biome scale. 
Quickly-changing and age-dependent fluxes were also found in a number of previous syntheses (Amiro et al. 2010 10.1029/2010JG001390, Magnani et al. 2007 10.1038/nature05847).

In contrast to most fluxes, $NEP$ is highest at intermediate ages

>>>>

Our study reveals that most C fluxes quickly increase to a plateau as stands age (Fig. 6), consistent with current understanding of age trends in forest C cycling [e.g., @anderson-teixeira_altered_2013].
*Quickly-changing and age-dependent fluxes were also found in a number of previous syntheses (Amiro et al. 2010 10.1029/2010JG001390, Magnani et al. 2007 10.1038/nature05847).*
While limited records in very young (*i.e.*, <5 year old) stands resulted in poor resolution of the earliest phases of this increase for many variables (sometimes detecting no age trend; Table 1), any autotrophic C flux (e.g., $GPP$, $NPP$ and its components, $R_auto$) would be minimal immediately following a stand-clearing disturbance.
These would be expected to increase rapidly with the most metabolically active components of biomass, foliage and fine roots, which also increase rapidly with stand age (Fig. 7).
In contrast, soil heterotrophic respiration ($R_{het-soil}$) and total soil respiration ($R_{soil}$) are expected to be non-zero following stand-clearing disturbance, although these may decrease with a reduction of root respiration ($R_{soil}$ only) and C exudates or increase in response to an influx of dead roots and litter [@ribeiro-kumara_how_2020; @mauer_carbon_2020; @bond-lamberty_contribution_2004].
In this study, we detect no significant age trends in either variable.

Notably, net carbon sequestration ($NEP$) increases with age up to the 100-yr threshold examined here, with more pronounced patterns in temperate than boreal forests (Fig. 6f). 
This finding is largely consistent with, but built from a far larger dataset than, previous studies showing an increase in $NEP$ across relatively young stand ages [**Pregitzer and Euskirchen (2004 http://dx.doi.org/10.1111/j.1365-2486.2004.00866.x); Baldocchi; Luyssaert**].
However, $NEP$ has been observed to decline from intermediate to old stands **[Luyssaert 2008]**, and the $NEP$ estimated by our model for 100-year-old temperate conifer stands (~5 Mg C ha^-1^ yr^-1^) exceeds the mean of mature forests in the same biome (0.7 Mg C ha^-1^ yr^-1^; Fig.4).
A decrease in $NEP$ is consistent with the observed decelleration of biomass accumulation as stands age, although both biomass and non-living C stocks will often continue to increase well beyond the 100-yr threshold used here to delimit young and mature stands (**REFS**).
